Checkpoint 4

### 2020-05-02 Draft-Report.Rmd
fed changes

Finaldata<-read_csv("time_series_final_Data.csv")

@@

```{r, warning=FALSE}
ggplotly(c)
```
This visualisation depicts the distribution of positive COVID-19 cases by region and by which political party won in the 2016 elections. We can see that Democrat states in the Midwest, Mountain, and West have a larger range and higher quantile metrics for positive cases overall. For the Northeast and South regions the mean of positive COVID-19 cases are higher but not significantly. This is an interesting pattern considering that poltical party affiliation appears to interact with the number of postive cases by region. 
\
\

@@

```{r}
Finaldata%>%
  ggplot(aes(x = ChinaVirusInterest))+
  geom_density()
```
During the 2020-03-14 - 2020-03-21 week, Trump in an official press announcement labeled the Corona Virus as "China Virus" and we wanted to see how his comments affected search patterns across states.

```{r}
Finaldata%>%
  filter(ChinaVirusInterest ==0)%>%
  group_by(Day)%>%
  summarize(n = n())
```

@@

```{r}
model_data<-
  Finaldata%>%
  mutate(Day=as.numeric(Day)-as.numeric(min(Day)))%>%
  select(ChinaVirusInterest, Day, percent_white, StateColor, positive)

@@

```{r}
set.seed(454)
model_1 <- stan_glm(
  ChinaVirusInterest ~ Day + percent_white+StateColor+positive,
  data = model_data, family = gaussian,
  chains = 4, iter = 10000, refresh = 0
)
model_1

@@

prediction_summary(y = model_data$ChinaVirusInterest,
  yrep = pred_1)
```
In this simple model, we see that the Mae value is 10.5, and 55% of the data points are within the 50% confidence interval, and 92% are within the 95% confidence interval. To be a simple model, it does a fairly good job at capturing the trends.

################ FEDDY PREDICT FOR FLORIDA TOO please. ALSO MOVE YOUR STUFF TO THE RIGHT PLACES ############

@@

```{r}
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

@@

### Feddy model eval (model 1)

@@

>>>>

Finaldata<-read_csv("time_series_final_Data.csv")
google<-read.csv("Google/googlefinal.csv")

@@

```{r, warning=FALSE}
ggplotly(c)
```
This visualisation depicts the distribution of positive COVID-19 cases by region and by which political party won in the 2016 elections. We can see that Democrat states in the Midwest, Mountain, and West have a larger range and higher quantile metrics for positive cases overall. For the Northeast and South regions the mean of positive COVID-19 cases are higher but not significantly. This is an interesting pattern considering that poltical party affiliation appears to interact with the number of postive cases by region.

```{r}
Finaldata%>%
  ggplot(aes(x = ChinaVirusInterest))+
  geom_density()
```
```{r}
Finaldata%>%
  filter(ChinaVirusInterest ==0)%>%
  group_by(Day)%>%
  summarize(n = n())
```
During the 2020-03-14 - 2020-03-21 week, Trump in an official press announcement labeled the Corona Virus as "China Virus" and we wanted to see how his comments affected search patterns across states.

@@

@@

```{r}
model_data<-
  Finaldata%>%
  mutate(Day=as.numeric(Day)-as.numeric(min(Day)))%>%
  select(ChinaVirusInterest, Day, percent_white, StateColor, positive, State)

@@

```{r results = "hide", include = FALSE}
set.seed(454)
model_1 <- stan_glm(
  ChinaVirusInterest ~ Day + percent_white+StateColor+positive,
  data = model_data, family = gaussian,
  chains = 4, iter = 10000, refresh = 0
)

@@

@@

```{r results = "hide", include = FALSE}
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

@@

### Feddy model eval (model 1)
```{r}
# Trace plots
mcmc_trace(model_1,pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day"),facet_args = list(ncol = 3, strip.position = "left"))

# Density plots
mcmc_dens_overlay(model_1, pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day"),facet_args = list(ncol = 3, strip.position = "left"))
```

As we can see in our mcmc plots,  we see that our chains are all close to each other meaning that our simulation was stable.

```{r}
model_1
```

prediction_summary(y = model_data$ChinaVirusInterest,
  yrep = pred_1)
```

In this simple model, we see that the Mae value is 10.5, and 55% of the data points are within the 50% confidence interval, and 92% are within the 95% confidence interval. To be a simple model, it does a fairly good job at capturing the trends.

new_data <- model_data %>% filter(State == "FL")
new_pred <- posterior_predict(
  model_1,
  newdata = new_data)

actual_FL_pred<-model_data %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))

actual_FL_pred
```

Our actual value in our simple model lies within the mean value of our prediction and it is close to the mean and the third quarter.

@@

### Normal Regression Model

new_data <- Finaldata %>% filter(State == "FL")
new_pred <- posterior_predict(
  model_1,
  newdata = new_data)

actual_FL_pred
```
